Replication of Hills 2009

### 2018-07-18 Main.Rmd
Progress on Hills replication

List of libraries
```{r echo=TRUE, warning=FALSE, message=FALSE}
library(purrr) # fp library
library(readr) # read text data files (csv, etc.)
library(ggplot2) # plotting
library(langcog) # useful things used by Language and Cognition Lab
library(boot) # functions for bootstrapping
library(dplyr) # for working with datafram-like objects
library(tidyr) # for data tidying
library(wordbankr) # access to wordbank data
library(directlabels) # direct labeling of data in plots
library(stringr) # common string operations
library(lmtest) #  diagnostic checking in linear regression models
library(rwebppl) # interface to probabilistic programming language WebPPL
library(jsonlite) # JSON parser
library(nlme) # gaussian linear and nonlinear mixed-effects models
library(feather) # read and write fast lightweight binary columnar data
library(broom) # converts R function outputs to tidy data frames
library(HDInterval) # calculate highest density intervals of objects w/ pdf
library(BBmisc) # misc helper functions
library(igraph) # network analysis and visualization
library(knitr) # general-purpose tool for dynamic report generation
library(lemon) # functions for working w/ ggplot2 and knitr extensions
library(tibble) # modern dataframes
library(doParallel)
library(networkD3)
```

>>>>

List of libraries
```{r echo=TRUE, warning=FALSE, message=FALSE}
library(purrr) # fp library
library(readr) # read text data files (csv, etc.)
library(ggplot2) # plotting
library(langcog) # useful things used by Language and Cognition Lab
#library(boot) # functions for bootstrapping
library(dplyr) # for working with datafram-like objects
library(tidyr) # for data tidying
library(wordbankr) # access to wordbank data
#library(directlabels) # direct labeling of data in plots
library(stringr) # common string operations
#library(lmtest) #  diagnostic checking in linear regression models
#library(rwebppl) # interface to probabilistic programming language WebPPL
#library(jsonlite) # JSON parser
#library(nlme) # gaussian linear and nonlinear mixed-effects models
#library(feather) # read and write fast lightweight binary columnar data
library(broom) # converts R function outputs to tidy data frames
#library(HDInterval) # calculate highest density intervals of objects w/ pdf
#library(BBmisc) # misc helper functions
library(igraph) # network analysis and visualization
library(knitr) # general-purpose tool for dynamic report generation
library(lemon) # functions for working w/ ggplot2 and knitr extensions
library(tibble) # modern dataframes
library(doParallel)
library(networkD3)
```

### 2018-07-18 Testing.Rmd
Progress on Hills replication

@@

### Large-Scale Structure of Networks

@@

Initial Clique Analysis
```{r}
age <- 20
g <- feature_networks[[age - 15]]
g <- delete.vertices(g, degree(g)==0)
res <- clique.community.opt(g,3)

@@

>>>>

```{r, setup, include=FALSE}
#knitr::opts_chunk$set(collapse = TRUE)
```

@@

@@

# Initial Cluster Analysis

## Clique Percolation
```{r}
age <- 20
g <- feature_networks[[age - 15]]
g <- delete.vertices(g, degree(g)==0)
res <- clique.community.opt(g,4)

@@

## Walktrap 
```{r}
age <- 20
g <- feature_networks[[age - 15]]
g <- delete.vertices(g, degree(g)==0)
res_w <- communities(cluster_walktrap(g))

## Paint them to different colors
colbar <- rainbow( length(res_w)+1 )
for (i in seq(along=res_w)) {
  V(g)[ res[[i]] ]$color <- colbar[i+1]
}

## Paint the vertices in multiple communities to red
V(g)[ unlist(res_w)[ duplicated(unlist(res_w)) ] ]$color <- "red"

## Plot with the new colors
plot(g, layout=layout_with_fr, vertex.label=V(g)$uni_lemma)
plt(res_w, g)
```
